---
title: "Projects"
---

This is a little project where I look at some data from Danish MP's Facebook data. It is from the year of 2020. The dataset has unique facebook posts from Danish MP's as the unit of observation.

```{r} #first I read in the necessary packages and data}
library(tidyverse)
X2020 <- read_excel("~/Facebook data/dkpolsome-main/dkpolsome-main/Omstrukturede datasæt/2020.xlsx")
```

First I look at what type posts generate the most comments. This plots shows the average number of comments per type of post.

```{r}
ggplot(X2020, aes(Comments, Type)) + 
  geom_bar(aes(fill = Type), stat = "summary", fun = "mean") + 
  labs (x = "Average amount of comments", y = "Type of posts") 
```

What if I wanted to look at different variables, and also would like to order the categories based on their average. This codes calls a function that creates the same plot. \

```{r}
# Calculate mean comments by post type
mean_comments <- aggregate(Comments ~ Type, data = X2020, FUN = mean)

# Order the types based on mean comments
mean_comments$Type <- reorder(mean_comments$Type, -mean_comments$Comments)
# Here I use a function to call a similar plot
create_barchart <- function(data, variable1, variable2) {
  data %>% 
    mutate({{variable1}} := fct_rev(fct_infreq({{variable1}}))) %>% 
    ggplot (aes(x = {{variable1}}, y = {{variable2}})) + 
    geom_bar(stat = "identity") + 
    theme_light()
}
create_barchart(mean_comments, Type, Comments)
```

\
This code produces a plot over the most popular politicians in terms of likes.

```{r}
#calculate the mean by page name
mean_likes <- aggregate(Likes ~ `Page Name`, data = X2020, FUN = mean)
#order the page names based on likes
mean_likes$`Page Name` <- reorder(mean_likes$`Page Name`, mean_likes$Likes)

# plot the most popular politicians
mean_likes %>% 
  top_n(10, Likes) %>% 
ggplot(aes(Likes, `Page Name`)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(x = "Average likes", y = "Politician")
```
